---
title: "Developing Data Products Wk 3"
author: "Michael O'Donnell"
date: "9 February 2020"
output: ioslides_presentation
---


## Outline

This notebook outlines the creation of a plotly plot, submitted for the Developing Data Products Coursera course, on Week 3. I have chosen to use a dataset from the Tidy Tuesday Project, more about which you can find [here](https://github.com/rfordatascience/tidytuesday).

The specific dataset is about songs, consisting of metadata taken from Spotify.

```{r setup, include=FALSE, message=FALSE}
library(tidyverse)
library(plotly)

spotify_songs <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')
```

## Plot Overview

This plot looks at the relationship between song popularity and song duration. We will also use a grouping on "playlist genre" to see if this has any relationship with the outcome.


## Plot
```{r plot, echo = FALSE, message=FALSE}
# let's create a ggplot and then build a ggplotly object from it

# downsample to impriove performance of our plot...
set.seed(1225)

spotify_songs_q <- spotify_songs %>% 
  sample_frac(0.2)


spotify_songs_q %>% 
  ggplot(aes(duration_ms/1000, 
             track_popularity,
             text = track_name)) +
  geom_point(aes(color = playlist_genre), alpha = 0.2) +
  scale_color_discrete(name = "Genre") +
  labs(x = "Song Duration (seconds)",
       y = "Song Popularity",
       title = "How does song duration and genre affect popularity?") -> p

p %>% ggplotly(tooltip = "text")
```


