---
title: "Week 2 Leaflet"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

*Produced on 14th January 2020*

# Outline

This notebook outlines the creation of a leaflet map, submitted for the Developing Data Products Coursera course, on Week 2. I have chosen to use a dataset from Ireland, the National Inventory of Architectural Heritage.

```{r}
library(tidyverse)
library(leaflet)
library(colorspace)


niah_data <- read_csv("http://dahg.maps.arcgis.com/sharing/rest/content/items/4b36c9a903f9463e8ccb460055698d72/data", locale = readr::locale(encoding = "latin1"))


```
The map being produced is of the architectural heritage of the county of Wicklow - the label on each has the initial building data and the popup describes the site. 
```{r produce_map}
#prep data - filter for descriptive info, coords, dates
niah_data %>% 
  select(NAME, COMPOSITION, COUNTY, APPRAISAL, LONGITUDE, LATITUDE, DATEFROM, DATETO) %>% 
  filter(COUNTY == "Wicklow")-> map_data

leaflet(map_data) %>% 
  addTiles() %>% 
  addCircles(popup = ~as.character(COMPOSITION),
             label = ~as.character(DATEFROM))
```

